---
title: "TSA Final Project - Forecasting Post-War Electricity Mix in Germany"
author: "Ayoung Kim, Lucy Wang"
output: pdf_document
geometry: margin=2.54cm
---

## Instructions to Complete your Project Report

### General Guidelines

1. Use Rmd for your final report.

2. Write in scientific style, not narrative style.

3. [Global options for R chunks](https://rmarkdown.rstudio.com/lesson-3.html) should be set so that only relevant output is displayed. Turn on/off messages and warnings when applicable to avoid unnecessary outputs on the pdf.

4. Make sure your final knitted PDF looks professional. Format tables, figures, chapters, etc.

5. Make sure you add a link to you Github repository in the final report. If you're using public data. Make the repository public. If using private data, make it private and please send me an invitation to collaborate. Otherwise, I will not be able to access your repository.

6. Make sure the PDF file has the file name "Lastname1_Lastname2_Lastname3_ENV797_Project.pdf" and submit it to Sakai under A09 - Final Project - Part III. You will only submit your PDF file. One submission per group.

### Contents of the Report 

#### Introduction, Motivation, Relevance, Objectives

Write a few paragraphs detailing the rationale for your study. This should include both the context of the topic as well as a rationale for your choice of dataset (reason for location, variables, etc.). You may choose to include citations if you like or any other reference you may have used during the project (optional).
1) Context of topic (Done)
2) Reason for location (Done), variables including the rationale for my choice of dataset (Done) 
3) Citations (Done)

Paragraph:
Several European countries, including Germany, had relied heavily on imported fossil fuels, particularly natural gas from Russia, before the Ukraine-Russia war broke out in February 2023 (Maliszewska-Nienartowicz, 2024). According to data on German gas imports in 2020 (BP), 55.2% of imported gas came from Russia (Umbach, 2022). However, the onset of the war disrupted the energy market across Europe, especially impacting Germany's energy supply. In response, Germany reactivated coal plants, shifting back from natural gas—considered a cleaner energy source—to coal (Luschini, Rego & Montebello, 2024). Significant changes in Germany’s energy mix and market were anticipated, and the energy crisis highlighted the urgent need for a transition to renewable energy to enhance energy security by reducing dependence on imported energy sources (Maliszewska-Nienartowicz, 2024).
In this context, we aimed to investigate how the Ukraine-Russia war (2023) actually affected Germany’s energy mix, particularly regarding Natural Gas and Renewables.

This project focused specifically on changes in Germany's electricity generation mix. Although Natural Gas plays a primary role in heating and cooling—accounting for 44% of total imported natural gas usage—this study sought to forecast how the role of Natural Gas may evolve in Germany’s electricity sector and the subsequent impacts on the adoption of Renewables post Ukraine-Russia war. 

Lucy: (Description - Energy Security, Policy & Market, Renewable Transition), Objectives 

Throughout this project, the analyses are based on monthly electricity production data from the International Energy Agency (IEA).

#### Dataset information

The entire analysis was based on the Monthly Electricity Production data from the International Energy Agency (IEA)'s Monthly Electricity Statistics iin csv (https://www.iea.org/data-and-statistics/data-product/monthly-electricity-statistics). 
The dataset consists of the following columns: Country, Time, Balance, Product, Value, and Unit. It contains monthly electricity mix data by energy source from January 2010 to December 2024, covering countries such as Australia, Denmark, Germany, Iceland, Ireland, Japan, and Korea, among others. In the "Product" column, energy sources include Hydro, Coal/Peat & Manufactured Gas, Oil and Petroleum Products, Natural Gas, and Total Renewables (comprising Hydro, Geothermal, Solar, Wind, and Other). Our team cleaned the dataset and filtered it to include only Germany, Total Renewables, and Natural Gas. All units are in GWh.

```{r, warning=FALSE, echo=FALSE}
library(knitr)

#Table 
summary_germany <- data.frame(
  Variable = c("Range", "Unit", "Central Tendency", "Source"),
  Natural_Gas = c("2010/01/01 - 2024/12/31", "GWh", "Mean: 6419.49", "IEA"),
  Renewables = c("2010/01/01 - 2024/12/31", "GWh", "Mean: 16835.20", "IEA")
)

kable(summary_germany, caption = "Summary Table for Energy Mix in Germany")
```
#### Analysis (Methods and Models) - Lucy 

Describe the analysis and tests that were performed. Described the components of the time series you identified. List any packages and functions used. Include visualizations of your dataset (i.e. time series plot, ACF, PACF, etc). 

Format your R chunks so that graphs are displayed but code is not displayed. Accompany these graphs with text sections that describe the visualizations and provide context for further analyses.

Each figure should be accompanied by a caption, and referenced within the text if applicable.

## Natural Gas Analysis

```{r packages, warning=FALSE, message=FALSE, echo=FALSE}
library(lubridate)
library(ggplot2)
library(forecast)  
library(Kendall)
library(tseries)
library(outliers)
library(tidyverse)
library(smooth)
library(zoo)
library(kableExtra)
```

### NG- Import data file 
```{r data file, echo=FALSE}
ng_data <- read.csv(
  file="./Data/IEA_MonthlyElectricityProduction_1224.csv",
  header=TRUE,
  skip=8) %>% 
  filter(Country=="Germany") %>% 
  filter(Product == "Natural Gas") %>% 
  mutate(Time = my(Time) ) %>% 
  arrange(Time) %>% 
  filter(Time>="2010-01-01")

```

### NG - MSTS 

```{r , echo=FALSE}
ng_ts <- msts(ng_data$Value, start = c(2010,1), seasonal.periods = c(12))

#check stationarity
adf.test(ng_ts)
```

p-value < 0.05. The time series is stationary. 

### NG - Initial Plots

```{r, echo=FALSE}
#Plot for Natural Gas
ng_ts_plot <- autoplot(ng_ts)+
  ylab("Natural Gas")

plot(ng_ts_plot)

#ACF and PACF plots
par(mfrow=c(1,2))
ACF_ng_plot <- Acf(ng_ts, lag = 40, plot = TRUE,main="ACF of Natural Gas")
PACF_ng_plot <- Pacf(ng_ts, lag = 40, plot = TRUE,main="ACF of Natural Gas")
par(mfrow=c(1,1))

ng_stl <- stl(ng_ts, s.window = "periodic")
autoplot(ng_stl) +
  ggtitle("STL Decomposition - NG")+
  theme_minimal()


```

```{r, message=FALSE, warning=FALSE, echo=FALSE}
#create a subset for training purpose
n_for = 12
ts_ng_train <- subset(ng_ts,
                      end = length(ng_ts)-n_for)

#create a subset for testing purpose
ts_ng_test <- subset(ng_ts,start = length(ng_ts)-n_for)

autoplot(ts_ng_train)
autoplot(ts_ng_test)
```

### NG - Model 1: STL + ETS

```{r ETS, echo=FALSE, message=FALSE, warning=FALSE}
#Fit and forecast STL + ETS model to data
ETS_ng <- stlf(ts_ng_train,h=12)

#Plot foresting results
autoplot(ETS_ng) + ylab("Production")


autolayer(ETS_ng, series="STL + ETS")+
  autolayer(ts_ng_train, series="observed", PI=FALSE, color="black")+
  ylab("Generation") + 
  ylim(10000,33000)+
  theme_minimal()

#Plot model + observed data
autoplot(ng_ts) +
  autolayer(ETS_ng, series = "STL + ETS", PI = FALSE) +
  ylab("Generation") +
  ggtitle("EST Model - Natural Gas")+
  theme_minimal()

#Plot model + observed data
autoplot(ng_ts) +
  autolayer(ETS_ng, series="STL + ETS",PI=FALSE) +
  ylab("Generation")+
  ggtitle("ETS Model - Natural Gas")+
  theme_minimal()

```

### NG - Model 2: ARIMA + FOURIER terms

```{r ARIMA, echo=TRUE, message=FALSE, warning=FALSE}
#Simple ARIMA 
ARIMA_ng<-auto.arima(ts_ng_train)
print(ARIMA_ng)

ARIMA_ng_forecast <- forecast(object = ARIMA_ng, h = 12)

autoplot(ng_ts) +
  autolayer(ARIMA_ng_forecast, series="ARIMA",PI=FALSE) +
  ylab("Generation")+
  theme_minimal()+
  ggtitle("ARIMA - NG")

ARIMA_f<- auto.arima(ts_ng_train, 
                             seasonal=FALSE, 
                             lambda=0,
                             xreg=fourier(ts_ng_train, 
                                          K=c(6))
                             )

#Forecast with ARIMA fit
#also need to specify h for fourier terms
ARIMA_f_forecast <- forecast(ARIMA_f,
                           xreg=fourier(ts_ng_train,
                                        K=c(6),
                                        h=12),
                           h=12
                           ) 

#Plot foresting results
autoplot(ARIMA_f_forecast) + ylab("Production")

#Plot model + observed data
autoplot(ng_ts) +
  autolayer(ARIMA_f_forecast, series="ARIMA_FOURIER") +
  autolayer(ts_ng_test, series="observed", PI=FALSE, color="black")+
  ylab("Generation")+
  theme_minimal() +
  ggtitle("ARIMA_FOURIER - Natural Gas")

#Plot combined results
autoplot(ng_ts) +
  autolayer(ARIMA_f_forecast, series="ARIMA_FOURIER")+
  autolayer(ts_ng_test, series="observed", PI=FALSE, color="black")+
  ylab("Generation") + 
  theme_minimal()+
  ggtitle("ARIMA_FOURIER - Natural Gas")
```

### NG - Model 3: TBATS

```{r TBATS, echo=FALSE, message=FALSE, warning=FALSE}
# TBATS can take time to fit
TBATS_ng_fit <- tbats(ts_ng_train)

TBATS_ng_forecast <- forecast(TBATS_ng_fit, h=12)

#Plot foresting results
autoplot(TBATS_ng_forecast) +
  ylab("Production") 

#Plot model + observed data
autoplot(ng_ts) +
  autolayer(TBATS_ng_forecast, series="TBATS",PI=FALSE)+
  ylab("Generation") 

#Plot combined results 
autoplot(ng_ts) +
  autolayer(TBATS_ng_forecast, series="TBATS")+
  autolayer(ts_ng_test, series="observed", color="black")+
  ylab("Generation") + 
  theme_minimal()+
  ggtitle("TBATS - Natural Gas")


```

### NG - Model 4: Neural Network Time Series Forecasts

```{r NNETAR, echo=FALSE, message=FALSE, warning=FALSE}

Neural_ng_fit <- nnetar(ts_ng_train,
                 p=1,
                 P=1,
                 xreg=fourier(ts_ng_train, K=c(2)))

Neural_ng_forecast <- forecast(Neural_ng_fit, 
                   h=12,
                   xreg=fourier(ts_ng_train, 
                                          K=c(2),h=12))


#Plot foresting results
autoplot(Neural_ng_forecast) +
  ylab("Production") 


#Plot model + observed data
autoplot(ng_ts) +
  autolayer(Neural_ng_forecast, series="Neural Network",PI=FALSE)+
  ylab("Production") 

#Plot combined results
autoplot(ng_ts) +
  autolayer(Neural_ng_forecast, series="Neural Network")+
  autolayer(ts_ng_test, series="observed", color="black")+
  ylab("Generation") + 
  theme_minimal()+
  ggtitle("NN - Natural Gas")

```

### NG - Checking accuracy of the forecast models

```{r, echo=FALSE}

#Model 1: STL + ETS
ETS_ng_scores <- accuracy(ETS_ng$mean,ts_ng_test)  

#Model 2: ARIMA + Fourier 
ARIMA_ng_scores <- accuracy(ARIMA_f_forecast$mean,ts_ng_test)

# Model 3:  TBATS 
TBATS_ng_scores <- accuracy(TBATS_ng_forecast$mean,ts_ng_test)

# Model 4:  Neural Network 
NN_ng_scores <- accuracy(Neural_ng_forecast$mean,ts_ng_test)

```

### Compare performance metrics
```{r, echo=FALSE}
# Make it a data frame
scores_load <- as.data.frame(
  rbind(ETS_scores, ARIMA_scores, TBATS_scores, NN_scores)
)
row.names(scores_load) <- c("STL + ETS", "ARIMA + Fourier", "TBATS", "Neural Network")

# Choose model with lowest RMSE
best_model_load <- which.min(scores_load[,"RMSE"])
cat("The best model by RMSE is:", row.names(scores_load[best_model_load,]), "\n")

# Create nice kable table
library(kableExtra)

kbl(scores_load,
    caption = "Forecast Accuracy for Daily Load",
    digits = array(5, ncol(scores_load))) %>%
  kable_styling(full_width = FALSE, position = "center", latex_options = "hold_position") %>%
  kable_styling(latex_options = "striped", stripe_index = best_model_load)

```

### Plotting everything together
```{r, echo=FALSE}
autoplot(ts_ng_test) +
  autolayer(ETS_ng, PI=FALSE, series="STL+ETS") +
  autolayer(ARIMA_f_forecast, PI=FALSE, series="ARIMA + Fourier") +
  autolayer(TBATS_ng_forecast,PI=FALSE, series="TBATS") +
  autolayer(Neural_ng_forecast,PI=FALSE, series="Neural Network") +
  ylab("Daily Active Power") +
  guides(colour=guide_legend(title="Forecast"))
```

#### Summary and Conclusions

*Final forecast under conclusions

Summarize your major findings from your analyses in a few paragraphs and plots. What conclusions do you draw from your findings? Any insights on how to improve the model?

## Final Forecast NG : ARIMA + Fourier is the best-fit model

```{r ARIMA, echo=FALSE, message=FALSE, warning=FALSE}

ARIMA_f_ng_final <- auto.arima(ng_ts, 
                                seasonal=FALSE, 
                                lambda=0,
                                xreg = fourier(ng_ts, K = c(6)))

# Future Values
Fourier_ng <- fourier(ng_ts, K = c(6), h = 12)

# Forecast using the same type of regressors
ARIMA_f_forecast_2025 <- forecast(ARIMA_f_ng_final, 
                                  xreg = Fourier_ng, 
                                  h = 12)

#Plot foresting results
autoplot(ng_ts)+
  autolayer(ARIMA_f_forecast_2025, series = "ARIM+FOURIER",PI=FALSE) +
  ylab("Generation")+
  ggtitle("Net Generation - Natural Gas (ARIMA+Fourier)")+
  theme_minimal()



#Plot model + observed data
autoplot(ng_ts) +
  autolayer(ARIMA_f_forecast_2025, series="ARIMA+FOURIER",PI=FALSE)+
  ylab("Generation") 

for_start = as.Date("2025-01-01") 
for_end = as.Date("2025-12-01")
for_period <- format(seq(as.Date(for_start), as.Date(for_end), by = "month"), "%b %Y")

ARIMA_ng_df <- tibble(Time = for_period, NetGen = ARIMA_f_forecast_2025$mean)
print(ARIMA_ng_df)
```

Ayoung: (Conclusion - NG)
Based on testing with four models—STL + ETS, ARIMA with Fourier terms, TBATS, and a Neural Network—it was found that the ARIMA model with Fourier terms provided the best fit for the natural gas data. While the STL + ETS model serves as a good baseline, it falls short in capturing more nuanced patterns, such as those present in natural gas generation. Due to the strength of the ARIMA model with Fourier terms in handling strong seasonality, this study assumed it would be the best-performing model. The results confirmed this assumption, as it achieved the lowest RMSE and MAE values among the models tested.

Although the TBATS model fit the training data well, its forecasts were erratic, suggesting possible overfitting. TBATS and STL + ETS models tended to overpredict more than the other models, as indicated by their higher ME values. In fact, all models slightly overpredicted on average, given that all ME values were positive. The Neural Network (NN) model appeared to be too complex for the natural gas dataset, with higher RMSE and MAE values implying overfitting and poor generalization.

The forecasted values for 2025 showed little change before and after the onset of the Russia-Ukraine war. The natural gas dataset exhibited strong, consistent seasonality throughout the years, seemingly following normal seasonal trends. Although this study initially assumed that the war would have a more significant impact, the actual effect on natural gas usage was less than expected.

In conclusion, this study found that natural gas is likely to maintain a stable role in Germany’s electricity grid mix. The Russia-Ukraine war did not appear to significantly affect the energy mix in terms of natural gas usage.


Lucy: (Conclusion - Renewables)

Ayoung: Limitations and Further Analysis 

One limitation of this study is that it focused solely on the electricity mix component of natural gas usage, excluding its role in heating, which accounts for approximately 44% of Germany’s imported natural gas consumption. This omission likely contributed to the observed minor changes in natural gas usage, as the impact on the electricity sector alone may not fully capture the broader implications of shifts in energy policy or geopolitical events.

For future research, it is recommended to conduct a comprehensive analysis of the heating sector, where more significant changes in natural gas usage are anticipated. Additionally, future studies should expand the scope to include an analysis of the overall electricity mix, incorporating other energy sources and relevant parameters to provide a more holistic understanding of the energy system.

Furthermore, it is suggested that future research explore forecasting not only the quantities of natural gas and renewable energy but also their price dynamics. This would provide deeper insights into market behavior and inform energy policy planning more effectively.

**AI was used to check grammar



#### Reference 
Maliszewska-Nienartowicz, J. (2024). Impact of Russia's invasion of Ukraine on renewable energy development in Germany and Italy. Utilities Policy, 87, 101731.

Luschini, A. C., Rego, E. E., & Montebello, N. (2024). How did the Russia–Ukraine war impact energy imports and electricity generation? A comparative analysis between Germany and the United Kingdom. The Electricity Journal, 37(3), 107396.

Umbach, F. (2022, September 8). Risks and requirements for German gas and energy policy. GIS Reports. https://www.gisreportsonline.com/r/german-gas-policy/



